**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-04-26 submission/manuscript.Rmd
results section updated

#### Random Forest classification models 
To identify OTUs that are distinct at each biogeographical site, we constructed several Random Forest machine-learning models built on OTU abundances. The first model we built to classify the lumen versus mucosal samples for the right and left sides, independently (Figure 4A). The constructed model used ((Xopt? need to follow up with this too)) features for the left and ((Xopt)) for the right. The models performed very well when classifying these samples (AUC X and Y).

Figure 4:
* 4A: Classifying lumen vs mucosal samples on each side (L vs L, R vs R)
* 4B: There are differentially abundant OTUs in lumen vs mucosa

#### Important OTUs 
- the Random Forest model lets us pick out features that dictate the classification model separation values

>>>>

#### Random Forest classification models identify important OTUs on each side
To identify OTUs that are distinct at each biogeographical site, we constructed several Random Forest machine-learning models built on OTU abundances. The first model we built to classify the lumen versus mucosal samples for the right and left sides, independently (Figure 4A). The constructed model used ((Xopt? need to follow up with this too)) features for the left and ((Xopt)) for the right. The models performed very well when classifying these samples (AUC X and Y). The OTUs that were most predictive of each site are identified by their greatest mean decrease in accuracy when removed from the model. For distinguishing the right lumen and mucosa, OTUs from the _Bacteriodes_, _Actinomyces_, _Psuedomonas_ and two OTUs from the _Enterobacteraceae_ genera were differentially abundant (Figure 4B). The model classifying the left lumen and mucosa identified OTUs from _Turicibacter_, _Anaerococcus_, _Finegoldia_, _Peptoniphilus_ and two OTUs from the _Anaerococcus_ genera that could distinguish lumen from mucosal samples (Figure 4B). These results indicate that there are fine differences between the different sites of the colon, and that these can be traced down to specific OTUs on each side.
